Draft 1

### 2020-06-04 More info to add.Rmd
Correction of Finger surface area, addition of new information.

>>>>

______________
Regarding the volume of saliva expelled per cough. 
Papers:

@Chabrelie2018 : Table1. Volume of saliva expelled per cough or sneeze (0.044 or 0.44 [mL]). Point value. Taken from multiple sources.

@Nicas2005: "Original article of particle size and volume, but no aparent 0.044 value in there" This is the one that Nicas2009 cites when it comes to past calculation. It also says the following "Duguid reported that a sneeze emits about 200- fold more particles than a cough."

@Adhikari2019: 0.044 value plus minus 10%, uniform, citing Nicas 2009.

@Nicas2009: "The number and size distri- bution of cough particles adhere to values presented in a previous analysis, and an estimated 0.044 mL of fluid (saliva) is emitted per cough." citing Nicas2005

### 2020-06-04 Paper.Rmd
Correction of Finger surface area, addition of new information.

#### Parameters table
| Parameter | Units | Description | Input values / Equation | Distribution | Reference and comments |  
|:--:|:--:|:--:|:--:|:--:|:--:|
| C~sp~ | Gene Copies/ml | Concentration of SARS-CoV-2 in sputum or saliva | log~10~ [4,4.8...] | ReSample | @Wolfel2020 @Pan2020 @Kim2020 @To2020, RT-PCR data from 9, 2, 2, and 23 patients with COVID-19|
| GC:TCID~50~ | - | Genome copies to infectious virus conversion factor | 10^2^-10^3^ | Uniform | @Ip2016, mean RT-PCR to TCID~50~ ratio of 708, 547, and 185 gene copies per TCID~50~ for seasonal A(H1N1), A(H3N2), and influenza B, respectively |
| V~slv/cgh~ | mL | Volume of saliva expelled per cough | |  | |
| N~cgh/min~ |min^-1^ | Number of caughs per minute  | 0.57(1)| Normal |@Leung2020, based on data of 17 individuals with seasonal CoV| 
|t~i~ | min |Time spend doing the activity *i* | [...] | Normal | This study. Activity ATM: 20 hours of observational data |
|x~i~| m | Inoculation distance for activity *i* | [...] | Point values | Assumed |
| k | PFU^-1^ | Parameter of the exponential dose-response| 0.00246(0.00098) | Normal | http://qmrawiki.org/experiments/sars |
| n | min~-1~ |Decay rate for surface *j*| [...] | Normal | @VanDoremalen2020, CoV-2 infectivity assays, 40% RH and 21-23°C |
| |  ||  | | |

@@

>>>>

#### Parameters table
| Parameter | Units | Description | Input values / Equation | Distribution | Reference and comments |  
|:--:|:--:|:--:|:--:|:--:|:--:|
| C~sp~ | Gene Copies/ml | Concentration of SARS-CoV-2 in sputum or saliva | log~10~ [4,4.8...] | ReSample | @Wolfel2020 @Pan2020 @Kim2020 @To2020, RT-PCR data from 9, 2, 2, and 23 patients with COVID-19|
| GC:TCID~50~ | - | Genome copies to infectious virus conversion factor | 10^2^-10^3^ | Uniform | @Ip2016, mean RT-PCR to TCID~50~ ratio of 708, 547, and 185 gene copies per TCID~50~ for seasonal A(H1N1), A(H3N2), and influenza B, respectively |
| V~slv/cgh~ | mL | Volume of saliva expelled per cough | 0.0484-0.0396 | uniform | @Nicas2009, volume = 0.044, @Adhikari2019, assumed uniform $\pm$ 10%|
| N~cgh/min~ |min^-1^ | Number of caughs per minute  | 0.57(1)| Normal |@Leung2020, based on data of 17 individuals with seasonal CoV| 
|t~ATM~ | min |Time spend doing the activity *i* | [...] | Normal | This study. Activity ATM: 20 hours of observational data |
|x~ATM~| m | Inoculation distance for activity *i* | [...] | Point value |  This study. Estimated based on activity ATM: 20 hours of observational data |
| k | PFU^-1^ | Parameter of the exponential dose-response| 0.00246, 0.00135, 0.00459 | Triangular | Data obtained from QMRA wiki http://qmrawiki.org/experiments/sars, based on 2 studies @DeAlbuquerque2006, @DeDiego2008, using the from 5th, 50th, and 95th percentiles as min, mode, and max |
| n~stl~ | min^-1^ |Decay rate in steel | [...] | Normal | @VanDoremalen2020, SARS-CoV-2 infectivity assays, 40% RH and 21-23°C |
| n~pl~ | min^-1^ |Decay rate in plastic | [...] | Normal | @VanDoremalen2020, SARS-CoV-2 infectivity assays, 40% RH and 21-23°C |
| TE~sh_stl~ | % | Transfer efficiency from surface (steel) to hand | Normal | 37.4 (16) | @Lopez2013, transfer efficiency of viruses (MS2) from surfaces to skin at 40-65% humidity | 
| TE~sh_pl~ | % | Transfer efficiency from surface (plastic) to hand | Normal | 79.5 (21.2) | @Lopez2013, transfer efficiency of viruses (MS2) from acrylic to skin at 40-65% humidity | 
| TE~hm~ | - | Transfer efficiency from hand to mucouse membrane | Normal | 0.201(0.063) | @Pitol2017, transfer efficiency of viruses (MS2) from hand to saliva | 
| A~sf~ | cm^2^ | Finger surface area |Uniform | 3.8-6.6 | Data from @Chabrelie2018 @ @Peters2009a @Sahmel2015 | 
| FSA~fm~ | - | Fractional surface area | Uniform | 0.5-0.8 | Assumed |

@@

Although not perfect, a risk assessment framework could be use to conduct a hazzard assessment. Since offices will need to re-open 
https://www.osha.gov/shpguidelines/hazard-Identification.html.

A more comprehensive model such as the models described elsewhere (REF), could potentially help elucidating the relative contribution of different expossure routes, and inform the population regading the most sensitive measures they could take given the particularities of the situation (e.g., air conditionated in offices)
